Bridging the Gap Between Visual and Analytical Machine Learning Testing

### 2023-09-26 report/esecfse24.tex
feat(report): 2023-09-26 17:02 updates

Visualisations are used throughout the ML development lifecycle. In the early stages of the ML development lifecycle, visualisations are extensively used for make sense of the data and understanding its statistical properties. During the model development phase, visualisations are used to summarise various metrics and summary statistics of the model's performance. Once the model is deployed in production, visualisations are used to continually monitor their performance and trigger a new training cycle once their performance drops below a certain threshold.

@@

This paper is organised as follows...

@@

@@

>>>>

Visualisations are used throughout the ML development lifecycle to test various properties of the ML system. In the early stages of the ML development lifecycle, visualisations are extensively used for make sense of the data and understanding its statistical properties. During the model development phase, visualisations are used to summarise various metrics and summary statistics of the model's performance. Once the model is deployed in production, visualisations are used to continually monitor their performance and trigger a new training cycle once their performance drops below a certain threshold.

Besides testing, information gained from ML visualisations have a profound influence in the design and implementation decisions taken for the next step of the ML pipeline. For instance, we may visualise the distribution of our training data and find that it is normally distributed. Based on this information, we may opt for a Linear Regression model which assumes normality in the underlying data. However, such decisions are violated once the ML system is deployed in production, where the data constantly changes as a reflect of the real world. Implicit expectations obtained from visualisations must therefore be translated to analytical tests that fail once our expectations regarding the ML system are no longer met.

% However, in a production ML setting, such decisions quickly become implicit expectations since data constantly evolve and changes, as a reflection of the real world. These implicit expectations must be translated to more explicit, analytical tests which fail when our assumptions and expectations no longer hold.

@@

% TODO This paper is organised as follows...

@@

During the empirical analysis conducted for this study, we found several instances of where the assertions were related to the visualisation above. However, they were not relevant to this study since they did not test the property of the data or the model.

@@

\subsection{Mining ML visualisations/notebooks}
% NOTE we can perform further analysis by mining jupyter notebooks, in particular the visualisations?
